Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-08 gibbs.tex
minor
intrmediate changes in model section

We propose a cascade desalination process to lower supernatant salinity, it is worth to note that we are not limited with this process only.
For this process the gel must be commpressed/decompressed in an \emph{open} and \emph{closed} system.

By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with an \textbf{infinite} reservoir of an aqueous solution.
%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.

By the \emph{closed system} we mean that the gel is equilibrated with a \textbf{finite} reservoir of an aqueous solution, in this case after equilibration the gel and the reservoir again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
Although, the number of ions and volume of gel and reservoir may vary, the total number of ions and the total volume are constant.

The compression of the gel in the \emph{open system} does not affect the salinity in the 
reservoir, thus the density of ions and their chemical potential outside the gel remains constant 
$\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}). 
On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.

In the both cases there is two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.

>>>>

We propose a cascade desalination process to lower supernatant salinity.
%it is worth to note that we are not limited with this process only.
For this process the gel must be commpressed/decompressed in an \emph{open} and \emph{closed} system.
By the \emph{open system} we mean that the gel is in thermodynamic equilibrium with huge, effectively \textbf{infinite}, reservoir of an aqueous solution. 
The gel freely exchanges ions with the reservoir, while their concentration in reservoir (and chemical potential) remains constant.
%, such that there are the same ion's chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. The number of  $\na$ and $\cl$ ions and gel volume $\Vgel$ are allowed to change.
By the \emph{closed system} we mean that the gel is in equilibrium with a \textbf{finite} reservoir of an aqueous solution. 
In this case the exchange of ions between the gel and the reservoir may affect their concentration in reservoir, whereas the  
%again have the same ions chemical potential, the same temperature, and desired pressure difference between the gel and the reservoir. 
%Although, the number of ions and volume of gel and reservoir may vary, 
the total number of ions (in gel and in reservoir) is constant.

Due to huge size of the reservoir, the compression of the gel in the \emph{open system} does not affect the reservoir salinity, $\cs =$ $\cna=$ $\ccl=$ $\text{Const}$ (\reffig{fig: open}), whereas the number of ions entrapped in the volume $\Vbox$ changes.
On the contrary, the compression of the gel in the \emph{closed system} changes the salinity in the reservoir, but the total number of $\na$ and $\cl$ ions in the gel and in the reservoir, \ie in the volume $\Vbox$ (\reffig{fig: closed}), remains constant.

%In both cases there are two coexisting systems with constant $\mu P T$ allowed to exchange particles and change volume, which is represented as Gibbs ensemble.
